---
title: "Moringa_Core_DS9_Lawrence_Ondieki_IP_WK12"
author: "Lawrence Ondieki"
date: "3 July 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The Context
A Kenyan entrepreneur has created an online cryptography course and would want to advertise it on her blog. She currently targets audiences originating from various countries. In the past, she ran ads to advertise a related course on the same blog and collected data in the process. She would now like to employ my services as a Data Science Consultant to help her identify which individuals are most likely to click on her ads.

## Define the Question
What are the factors that can determine if a visitor to a site will click on an advertisement.

## Metric of Success
Identify the top factors that can determine if a visitor will click on an advertisement.

## The Experimental Design
1. Data was sourced from http://bit.ly/IPAdvertisingData. <br>
2. R was used as the analysis tool.<br>
3. An R-Markdown and HTML documents will be delivered <br>

# Exploratory Data Analysis (EDA)

## Import the data and look at the first six rows
```{r}
# Import the data and look at the first six rows
advertising <- read.csv(file = 'advertising.csv',stringsAsFactors = FALSE)
head(advertising)
```
### Check the data composition at a high level
```{r}
str(advertising)
```
### Data Column Names
```{r}
colnames(advertising)
```
## Appropriateness of the available data to answer the given question.
Given that the data was collected from the recent campaign, it is assumed to be appropriate for this research.<br>
The data is anonymized.


## Check for any missing values
```{r}
colSums(is.na(advertising))
```
<br>
There are no missing values.

# Univariate Analysis - Daily Time Spent On Site
```{r}
Daily_Time_Spent_on_Site <- advertising$Daily.Time.Spent.on.Site
par(mfrow=c(1,2),pin=c(3,2.5)) # Set the plotting area into a 1 * 2 array
boxplot(advertising$Daily.Time.Spent.on.Site,horizontal=TRUE,main="Box Plot")
hist(Daily_Time_Spent_on_Site,main="Histogram")
```
<br>
There are no outliers but Daily Time Spent On Site is right-skewed.

# Univariate Analysis - Area Income
```{r}
par(mfrow=c(1,2),pin=c(3,2.5))
Area_Income <- advertising$Area.Income
boxplot(Area_Income, horizontal = TRUE, main="Box Plot")
hist(Area_Income, main="Histogram")
```
<br>
Area Income has outliers for low income and right skewed.

# Univariate Analysis - Daily Internet Usage
```{r}
Daily_Internet_Usage <- advertising$Daily.Internet.Usage
par(mfrow=c(1,2),pin=c(3,2.5)) # Set the plotting area into a 1 * 2 array
boxplot(Daily_Internet_Usage,horizontal=TRUE,main="Box Plot")
hist(Daily_Internet_Usage,main="Histogram")
```
<br>
Daily Internet Usage has no outliers and fairly distributed.

# Univariate Analysis - Gender

```{r}
Male <- advertising$Male
Clicked_On_Ad <- advertising$Clicked.on.Ad
par(mfrow=c(1,2),pin=c(3,2.5)) # Set the plotting area into a 1 * 2 array
pie(table(Male),col=c("purple","cyan"),labels=c("Female", "Male"), main="Composition by Gender")
pie(table(Clicked_On_Ad),col=c("red","green"),labels=c("No", "Yes"), main="Clicked on Advert")
```
<br>
The dataset had slightly more females than males.<br>
There was an equal number of clicks and no-clicks (50% -50%).

```{r}
Male <- advertising$Male
table(Male)
```
```{r}
Clicked_On_Ad <- advertising$Clicked.on.Ad
table(Clicked_On_Ad)
```
```{r}
clicked.freq.matrix <- table(advertising$Male,advertising$Clicked.on.Ad)
clicked.freq.matrix
```
# Univariate Analysis - Frequency distribution of Clicks

```{r}
par(pin=c(5.5,1))
barplot(clicked.freq.matrix,beside=TRUE,las=1, horiz=TRUE, main="Advert Click counts by Gender", col=c("purple", "cyan"), names.arg=c("No_Click","Clicked"),legend.text=c("female","male"), args.legend=list(x="center"))
```
<br>
There were more advert clicks from females than from male.

# Multivariate analysis - all numerical variables
## Correlation matrix
```{r}
res <- cor(advertising[,c(1,2,3,4,7,10)])
res
```
## Load correlation plot library 
```{r}
library(corrplot)
```
## Plot the correlation
```{r}
corrplot(res, type="upper", order="hclust", tl.col="black", tl.srt=45)
```
<br>

## Important features to determine a click on an advertisement:-

1. Daily Internet Usage.<br>
2. Daily Time Spent on the site.<br>
3. The Area Income.<br>

```{r}
library("PerformanceAnalytics")
```

```{r}
chart.Correlation(advertising[,c(1,2,3,4,7,10)], histogram = TRUE, pch=19)
```

# Conclusion

Important features to determine a click on an add:- <br>

1. Daily Internet Usage.<br>
2. Daily Time Spent on the site.<br>
3. The Area Income.<br>

# Recommendations
Focus on adding content to site to keep visitors coming and staying longet on the site and on high income area.